### 2021-02-19 math/ia_2021/paper/paper.tex
math ia

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
    \vspace*{4cm}
        Comparing the speed of two methods of approximating the value of $\pi$ ---
        a computational approach\\
    \vspace{1cm}
    To what extent can a method of approximation of the value $\pi$ be computationally more efficient than another? \\
    \vspace{4cm}
    Word count: 2122
    \vfill
    \vspace{0.1cm}
    \end{center}
    \end{titlepage}

@@

% Just testing sections.. 
\newpage
\include{sections/Implementation}

>>>>

% Suppresses headers, footers, and page numbers on title page
\begin{titlepage}
    \begin{center}
    \vspace*{4cm}
    A statistical approach to predicting a tsunami’s wave height \\
    \vspace{1cm}
    Can the height of a tsunami's wave be predicted based on the distance from and 
    the magnitude of a preceding earthquake? \\
    \vspace{4cm}
    Word count: TBD
    \vfill
    \vspace{0.1cm}
    \end{center}
    \end{titlepage}

@@
